Untitled

### 2017-02-08 Code/calculate_std_mort_rates.Rmd

```{r load_libraries}
library(dplyr)
library(purrr)
library(ggplot2)
library(stringr)
library(reshape2)
library(grid)
library(gridExtra)
```

```{r}
load("~/BW_results/results_set_1.Rdata")
r.All.set1 <- r.All %>% filter(post.samp %in% c(1,2))

@@

```{r merge}
r.All.post1.2 <- merge(r.All.post1.2, std.pop, by = "age_minbin")

mortality.rates <- r.All.post1.2 %>% 
  group_by(post.samp, state.n, year.n, race.n, sex.n, COD) %>% 
  arrange(age_minbin) %>%
  summarise(age.std.mortality.rate = sum(age.weight*smoothed_rate),
            race = first(race),
            sex = first(sex),
            state = first(state))

ggplot(subset(mortality.rates, post.samp == 1 & state == "Alabama"), aes(y = age.std.mortality.rate, x = year.n)) + 
  geom_line(aes(col = COD)) + facet_grid(race ~ sex)

write.csv(r.All.post1.2, "~/BlackWhiteMortalityGap/Data/states_combined_post_samp_1_2.csv")
write.csv(mortality.rates, "~/BlackWhiteMortalityGap/Data/mortality_rates.csv")
```

>>>>

```{r load_libraries}
library(dplyr)
library(purrr)
library(ggplot2)
library(stringr)
library(reshape2)
library(grid)
library(gridExtra)

source("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Code/life_expectancy_functions.R")

```

```{r read_in_posterior_results_samples_1_and_2}
#this take a long time (a few hours!)
load("~/BW_results/results_set_1.Rdata")
r.All.set1 <- r.All %>% filter(post.samp %in% c(1,2))

@@

```{r merge_and_calculated_age_stdized_mortality}
r.All.post1.2 <- merge(r.All.post1.2, std.pop, by = "age_minbin")

#returns dataset with new variable "age.std.mortality.rate" 
mortality.rates <- r.All.post1.2 %>% 
  group_by(post.samp, state.n, year.n, race.n, sex.n, COD) %>% 
  arrange(age_minbin) %>%
  summarise(age.std.mortality.rate = sum(age.weight*smoothed_rate), #the sum is across age bins
            race = first(race),
            sex = first(sex),
            state = first(state))

```

```{r tidy_mortality.rates}
COD.levels <- c("Cardiovascular", "Cancers", "Communicable", 
                "Non-communicable", "Injuries", "All other causes")

mortality.rates$COD <- factor(mortality.rates$COD, COD.levels)

mortality.rates <- add_Census_Division(mortality.rates, state)
mortality.rates <- add_Census_Region(mortality.rates, state)
mortality.rates$stabbrs <- state.abb[match(mortality.rates$state, state.name)]
mortality.rates$year <- mortality.rates$year.n + 1968
mortality.rates$rate.per.100k <- mortality.rates$age.std.mortality.rate*100000
```

```{r save_mortality_dataset}
#write.csv(r.All.post1.2, "~/BlackWhiteMortalityGap/Data/states_combined_post_samp_1_2.csv")
write.csv(mortality.rates, "~/BlackWhiteMortalityGap/Data/mortality_rates.csv")
```
